---
title: "Scopus cienciometría"
output: html_notebook
---

# Creating environment 

```{r message=FALSE, warning=FALSE}
source("scripts/scopus.R")
```

# Getting data

En esta parte se carga el archivo

```{r message=FALSE, warning=FALSE}
paper <- tos_scopus("data/scientometrics_465.bib")
```

## Importance 

In this part, you will suport your research topic through a scientometrics analysis. Bibliometrix package helps us with it, please cite it in your paper 

Aria, M. & Cuccurullo, C. (2017). bibliometrix: An R-tool for comprehensive science mapping analysis, Journal of Informetrics, 11(4), pp 959-975, Elsevier, DOI: 10.1016/j.joi.2017.08.007

### Anual scientific production 

```{r}
paper$pccion_anual$anual_pccion
```


### Most productive autors

```{r warning=FALSE}
paper$pccion_anual$author_pccion
```


### Most popular journals 

## Evolution Tree of Science

This part shows the papers through the analogy of a tree 

```{r warning=TRUE}
paper$tos
```

## Subareas of your topic

This figure shows the amount of papers for each cluster. It will help you to select the subareas. 

```{r warning=FALSE}
paper$subareas$tipping_poing
```

The graph with the subareas selected

```{r}
plot(paper$subareas$graph_subareas_network,
         vertex.color=V(paper$subareas$graph_subareas_network)$color,
         vertex.label = "", 
         layout = layout.fruchterman.reingold)
```


this is the table of subarea 1

```{r warning=FALSE}
paper$subareas$subarea_1
```

This is the table of subarea 2 

```{r}
paper$subareas$subarea_2
```

This is the table of subarea 3 
```{r}
paper$subareas$subarea_3
```





